Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-04-20 analysis/paper/shceof.Rmd
Quita patchwork y purrr

library(metR)
library(data.table)
library(magrittr)
library(ggplot2)
library(tagger)
library(ggperiodic)
library(patchwork)
library(kableExtra)
library(shceof)

>>>>

library(metR)
library(data.table)
library(magrittr)
library(ggplot2)
library(tagger)
library(ggperiodic)
# library(patchwork)
library(kableExtra)
library(shceof)
